---
title: "NEWS"
author: Erik.Leppo@tetratech.com and jon.harcum@tetratech.com
output: github_document
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```



# baytrends 0.1.0.9006

* refactor: Corrected beta logit transformation, Issue #2 
    + fun_beta_logit.R

# baytrends 0.1.0.9005

* feature: Add new functions and checked with Check Package
    + fun_cb4d_buildout_01.R

# baytrends 0.1.0.9004

* refactor: Update NEWS install section and format, Issue #1

# baytrends 0.1.0.9003

* docs: Update package documentation
    + DESCRIPTION
    + NEWS
    + README
    + License (MIT)
* functions: Add new function files
    + fun_beta_logit.R
    + fun_cb4d_buildout_00.R
    + fun_mapping.R
    + tidBIT.R
* style: Add style to functions
    + Wrap text at 80 lines
    + Denote ending braces for functions
* documentation: Run CMD check and fix issues
    + Add packages to DESCRIPTION
    + Add bindings for global variables for functions
    + Add missing ImportFrom functions

# baytrends 0.1.0.9002

* docs: Add issue templates to repository

# baytrends 0.1.0.9001

* Create Repository on GitHub
